Quantifying the importance of a tree prior in Bayesian phylogenetics

### 2019-04-04 article.tex
Fix

% RJCB: I think this title is better: 
% (1) tree prior importantance is the goal, the error is just the means
% (2) no need to specify BEAST2, it's also just a means
\title{
  pirouette:
  Quantifying the importance of a tree prior in Bayesian phylogenetics
}
% \title{pirouette: Determining the error BEAST2 makes in inferring a phylogeny}

@@

We run \verb;pirouette (listing~\ref{lst:pir_run}) 
and plot the results (listing~\ref{lst:pir_plot}).
The resulting figure is shown in figure~\ref{fig:example_2}.
In this case, the inference model with a JC69 site model, 
strict clock model and Yule tree prior has the highest likelihood
amongst all candidates (table \ref{tab:evidences_example_2} shows
the evidences).

>>>>

% RJCB: I think this title is better: 
% (1) tree prior importance is the goal, the error is just the means
% (2) no need to specify BEAST2, it's also just a means
\title{
  Quantifying the importance of a tree prior in Bayesian phylogenetics
}
% \title{pirouette: Determining the error BEAST2 makes in inferring a phylogeny}

@@

We run \verb;pirouette; (listing~\ref{lst:pir_run}) 
and plot the results (listing~\ref{lst:pir_plot}).
The resulting figure is shown in figure~\ref{fig:example_2}.
In this case, the inference model with a JC69 site model, 
strict clock model and Yule tree prior has the highest likelihood
amongst all candidates (table \ref{tab:evidences_example_2} shows
the evidences).
